---
title: "Writing Functions"
author: "Lanette Tyler"
format: html
editor: visual
---

## Writing Functions

Normal approximation of the binomial distribution:
```{r}
n <- 40
prob <- 0.3
# probabilities from a binomial random variable
dbinom(0:n, size = n, prob = prob)
plot(0:n, dbinom(0:n, size = n, prob = prob), type = "h")
norm_x <- seq(from = 0, to = 40, length = 1000)
lines(norm_x, dnorm(norm_x,mean = n*prob, sd = sqrt(n*prob*(1 - prob))))
```

We want to write a function that will take in a sample size and a probability and output a graph like this one above.

```{r}
plot_norm_appx <- function(n, prob) {
  plot(0:n, dbinom(0:n, size = n, prob = prob), type = "h")
  norm_x <- seq(from = 0, to = 40, length = 1000)
  lines(norm_x, dnorm(norm_x,mean = n*prob, sd = sqrt(n*prob*(1 - prob))))
}
```

Test out our function:
```{r}
plot_norm_appx(30, 0.5)
```
Make the function more user friendly by adding defaults:
```{r}
plot_norm_appx <- function(n = 30, prob = 0.5) {
  plot(0:n, dbinom(0:n, size = n, prob = prob), type = "h")
  norm_x <- seq(from = 0, to = 40, length = 1000)
  lines(norm_x, dnorm(norm_x,mean = n*prob, sd = sqrt(n*prob*(1 - prob))))
}
```

Test it out:
```{r}
plot_norm_appx()
plot_norm_appx(n = 50)
plot_norm_appx(prob = 0.1)
```

Make a simple funtion to take in a data frame and print it out. Make a data frame and test it out.
```{r}
bp_rater <- function(d_frame) {
  d_frame
}
column1 <- seq(1:20)
column2 <- letters[1:20]
practice_df <- data.frame(column1, column2)
practice_df
bp_rater(practice_df)
```

Now try two data frames:
```{r}
bp_rater <- function(data_frame1, data_frame2) {
  list_of_dfs <- list(c("BP Before" = data_frame1,"BP After" = data_frame2))
  list_of_dfs
}
column1 <- seq(11,30)
column2 <- letters[7:26]
practice_df2 <- data.frame(column1, column2)
bp_rater(practice_df,practice_df2)
```

