---
title: "R Objects, Workflow, and Functions"
author: "Lanette Tyler"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

## Vectors

Create a Vector

```{r}
set.seed(42)
my_runif <- runif(30)
is.vector(my_runif)
```

Subset object my_unif

```{r}
my_runif[1:10]
my_runif[c(1:3,15:17)]
```

Sort the vector (my_unif)

```{r}
sort(my_runif)
```

Create a vector with character strings in it and explore sorting conventions

```{r}
char_vector <- c("hix","abd","z4","xyz","42t","Xyz")
sort(char_vector)
```


## Data Frames

List data sets currently loaded into environment:
```{r}
data()
```
List of data sets in environment opens in a file (R data sets)

Load trees data set into environment:
```{r}
data(trees)
```
Loads into environment as "promise"

Output data set:
```{r}
trees
```
Outputs to console or qmd file, depending on settings; changes from "promise" to listed in env

Figure out the type of R object:
```{r}
str(trees)
```
It's a data frame!

Subset a column (two ways):
```{r}
trees$Height
trees[,2]
```
ouput columns (both are the same)

Get attributes from the data frame, especially names, names lists are output as vectors, so we can subset those vectors:
```{r}
attributes(trees)
names(trees)
colnames(trees)
names(trees)[2:3]
```







